Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-05-14 ltx/data_paper/DataPaper.tex
minor edits

\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1}^b \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \\	

@@

From \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance covariance estimates clearly represent maxima of the $\mathcal{Q}$-function. 

>>>>

\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1}^b \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \\	

@@

From \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance variance estimates clearly represent maxima of the $\mathcal{Q}$-function. 
